Financialisation of Commodity Markets \\\large{Co-movement Behind-the-Scenes}

### 2025-08-25 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@44a69cd7b8d55bcede84743b6529d25e5e1d6a41 🚀

\newgeometry{margin=.75in}

@@

\caption{\label{fig-regimes}This figure compares estimates for mean (top
panel) and volatility (bottom panel) for individual commodity returns
between \textbf{CHP} regime phases (\textbf{backwardation}
vs.~\textbf{contango}) for the four periods. Each stacked bar shows how
many cases fall into two categories: yellow (the estimate for the
\textbf{backwardation phase} is smaller than for the \textbf{contango}
phase) and blue (the estimate for the \textbf{backwardation phase} is
greater than for the \textbf{contango} phase); numbers inside the bars
indicate the count of observations in each category.
\textbf{Backwardation} and \textbf{contango} regimes as well as period
definitions are discussed in @sec-methods while the results are
discussed in @sec-results.}

@@

\begin{longtable}[t]{>{}l>{}r>{}r>{}r>{}r>{}r}

\caption{\label{tbl-stats-regime-tests}This table shows mean returns and
volatilities for the individual commodities and two equally weighted
portfolios of US and GB traded assets for the four periods. For each
period, estimates are computed independently over the whole
period--figure shown--as well as over phases of \textbf{backwardation}
(b) and \textbf{contango} (c)--results in brackets. The table further
shows the results of t-tests of significance for the mean returns
computed over the whole periods and t-tests of difference between these
when computed over the two phases independently along with F-tests of
difference for the corresponding variances. Values significant at the
1\%, 5\% and 10\% level are marked with ***, ** and * respectively.
Detailed results are available in the attached
\href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.
\textbf{Backwardation} and \textbf{contango} regimes as well as period
definitions are discussed in Section~\ref{sec-methods} while the results
are discussed in Section~\ref{sec-results}.}

@@

\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
\textbf{Corn-\#2 yellow (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.48\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{21.37\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{6.89\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-4.51\% (b<c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{29.54\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{36.15\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{21.8\% (b<c*)}}\\
\textbf{Oats (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{5.49\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{21.62\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{8.89\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-0.87\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.22\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{31.04\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{34.67\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{29.5\% (b>c***)}}\\
\textbf{Soybean meal (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{7.29\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{12.06\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{8.12\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-0.33\% (b<c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.34\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{32.55\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{31.78\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{25.11\% (b<c)}}\\
\textbf{Soybean oil (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{6.21\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{15.57\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{4.04\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-7.39\% (b<c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.43\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{28.35\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{25.75\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.95\% (b<c**)}}\\
\textbf{Soybeans (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{6.89\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{13.36\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{6.19\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-3.82\% (b<c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.47\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{30.04\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{28\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{21.22\% (b>c*)}}\\
\textbf{Wheat-SRW (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{5.07\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{17.63\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{6.68\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-1.58\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.93\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{33.03\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{37.62\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{26.58\% (b<c)}}\\
\textbf{Cattle-feeder (XCME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{0.39\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{7.43\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{7.13\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{1.87\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.23\% (b<c*)}} & \textcolor[HTML]{4285f4}{\textbf{15.16\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{15.24\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.69\% (b>c***)}}\\
\textbf{Cattle-live (XCME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.45\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{8.77\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{4.13\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{1.92\% (b<c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.1\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{17.43\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{16.32\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.3\% (b>c***)}}\\
\textbf{Lean hogs (XCME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{0.73\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{8.4\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{12.69\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-1.09\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.33\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{31.89\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{30.37\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{36.94\% (b<c*)}}\\
\textbf{Cocoa (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.66\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{16.35\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{1.39\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{3.65\% (b<c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.66\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{29.99\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{31.03\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{24.69\% (b>c**)}}\\
\textbf{Coffee-C (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{-5.91\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{20.38\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{2.2\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{1.99\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.84\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{32.3\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{30.17\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{31.86\% (b<c)}}\\
\textbf{Cotton-\#2 (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.24\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{0.95\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{12.53\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{0.5\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.38\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{29.01\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{33.26\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{20.61\% (b>c*)}}\\
\textbf{Lumber (XCME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{1.9\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-3.58\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{11.74\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{5.06\% (b>c**)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.58\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{29.39\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{36.31\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{25.1\% (b<c***)}}\\
\textbf{Orange juice (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{1.67\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{13.87\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{14.4\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{3.8\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.5\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{33.01\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{34.43\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{29.37\% (b<c)}}\\
\textbf{Sugar-\#11 (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{-4.56\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{24.87\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{11.82\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-1.16\% (b<c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.88\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{33.25\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{37.9\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{28.72\% (b<c*)}}\\
\textbf{Natural gas (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{35.38\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{16.25\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{0.93\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{8.33\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{61.55\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{54.6\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{53.58\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{44.58\% (b<c**)}}\\
\textbf{Crude oil-WTI (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{15.43\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*28.74\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{9.67\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-5.64\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.87\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{32.56\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{42.84\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{34.69\% (b<c***)}}\\
\textbf{Gasoline (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{16.65\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{30.95\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{10.59\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-5.37\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.77\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{41.76\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{40.07\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{37.09\% (b<c***)}}\\
\textbf{Heating oil (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{16.31\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*29.88\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{6.83\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-3.44\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.75\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{35.09\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{33.17\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{30.56\% (b<c***)}}\\
\textbf{Copper (XCEC)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{1.45\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*28.15\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{6.19\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-0.1\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.23\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{31.89\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{34.91\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{19.56\% (b<c***)}}\\
\textbf{Gold (XCEC)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{4.5\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{14.35\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{14.01\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{0.53\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.14\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.89\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{21.46\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{14.41\% (b<c***)}}\\
\textbf{Palladium (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{9.12\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{9.03\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*29.12\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{13.75\% (b>c*)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.27\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{32.71\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{36.14\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{25.38\% (b<c***)}}\\
\textbf{Platinum (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{12.93\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{10.56\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{7.29\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-7.92\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.62\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{22.66\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{25.53\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{19.48\% (b<c***)}}\\
\textbf{Silver (XCEC)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{6.19\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{17.54\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{21.96\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-2.43\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{33.92\% (b<c*)}} & \textcolor[HTML]{4285f4}{\textbf{39.87\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{24.35\% (b<c***)}}\\
\textbf{Aluminium (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{1.13\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{13.78\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-3.58\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{3.15\% (b>c**)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.6\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{26.41\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{26.48\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.56\% (b>c)}}\\
\textbf{Copper (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{0.45\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{**28.59\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{5.74\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{0.03\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.25\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{31.09\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{34.27\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.92\% (b<c***)}}\\
\textbf{Lead (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.83\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{28.99\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{10.74\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{2.07\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.64\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{41.74\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{41.05\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{23.26\% (b>c)}}\\
\textbf{Nickel (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{19.31\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{12.5\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{3.52\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{0.31\% (b>c***)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.26\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{44.27\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{41.45\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{28.98\% (b>c)}}\\
\textbf{Tin (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{4.07\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{*29.1\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{7.46\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{1.68\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.38\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{31.71\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{35.61\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.79\% (b<c***)}}\\
\textbf{Zinc (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{-4.52\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{20.13\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{7.62\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{9.07\% (b>c*)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.73\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{38.77\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{36.17\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{23.25\% (b<c**)}}\\
\textbf{US commodities} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{*6.89\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{**15.89\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{9.39\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-0.18\% (b>c)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{13.62\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{17.58\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{9.86\% (b<c***)}}\\
\textbf{GB commodities} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{2.47\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*21.77\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{5.25\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{2.72\% (b>c**)}}\\
\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.66\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{26.91\% (b<c*)}} & \textcolor[HTML]{4285f4}{\textbf{30.24\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{16.19\% (b<c***)}}\\

@@

\restoregeometry

>>>>

@@

\caption{\label{fig-regimes}This figure compares estimates for mean (top
panel) and volatility (bottom panel) for individual commodity returns
between \textbf{CHP} regime phases (\textbf{backwardation}
vs.~\textbf{contango}) for the four periods. Each stacked bar shows how
many cases fall into two categories: yellow (the estimate for the
\textbf{backwardation phase} is smaller than for the \textbf{contango}
phase) and blue (the estimate for the \textbf{backwardation phase} is
greater than for the \textbf{contango} phase); numbers inside the bars
indicate the count of observations in each category.
\textbf{Backwardation} and \textbf{contango} regimes as well as period
definitions are discussed in Section~\ref{sec-methods} while the results
are discussed in Section~\ref{sec-results}.}

@@

\caption{\label{tbl-stats-regime-tests}This table shows mean returns and
volatilities for two equally weighted portfolios of US and GB traded
assets for the four periods. For each period, estimates are computed
independently over the whole period as well as over phases of
\textbf{backwardation} and \textbf{contango}. The table further shows
the results of t-tests of significance for the mean returns as well as
t-tests of difference between these when computed over the two phases
independently along with F-tests of difference for the corresponding
variances. Values significant at the 1\%, 5\% and 10\% level are marked
with ***, ** and * respectively. Detailed results are available in the
attached \href{https://bautheac.shinyapps.io/co-movement/}{Internet
Appendix}. \textbf{Backwardation} and \textbf{contango} regimes as well
as period definitions are discussed in Section~\ref{sec-methods} while
the results are discussed in Section~\ref{sec-results}.}

@@

\toprule
\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
\midrule
\textbf{US commodities} & \textbf{mean} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{*6.89\%}} & \textcolor[HTML]{4285f4}{\textbf{**15.89\%}} & \textcolor[HTML]{4285f4}{\textbf{9.39\%}} & \textcolor[HTML]{4285f4}{\textbf{-0.18\%}}\\
\textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{***15.44\%}} & \textcolor[HTML]{4285f4}{\textbf{*15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{13.4\%}} & \textcolor[HTML]{4285f4}{\textbf{6.82\%}}\\
\textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{-1.09\%}} & \textcolor[HTML]{4285f4}{\textbf{*16.16\%}} & \textcolor[HTML]{4285f4}{\textbf{4.9\%}} & \textcolor[HTML]{4285f4}{\textbf{-6.33\%}}\\
\textbf{} & \textbf{} & \textbf{backwardation vs. contango} & \textcolor[HTML]{4285f4}{\textbf{**}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
\textbf{} & \textbf{volatility} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
\addlinespace
\textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{9.88\%}} & \textcolor[HTML]{4285f4}{\textbf{14.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.59\%}}\\
\textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{10.09\%}} & \textcolor[HTML]{4285f4}{\textbf{13.05\%}} & \textcolor[HTML]{4285f4}{\textbf{19.98\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}}\\
\textbf{} & \textbf{} & \textbf{backwardation vs. contango} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{**}} & \textcolor[HTML]{4285f4}{\textbf{***}} & \textcolor[HTML]{4285f4}{\textbf{***}}\\
\textbf{GB commodities} & \textbf{mean} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.47\%}} & \textcolor[HTML]{4285f4}{\textbf{*21.77\%}} & \textcolor[HTML]{4285f4}{\textbf{5.25\%}} & \textcolor[HTML]{4285f4}{\textbf{2.72\%}}\\
\textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{4.41\%}} & \textcolor[HTML]{4285f4}{\textbf{8.01\%}} & \textcolor[HTML]{4285f4}{\textbf{15.06\%}} & \textcolor[HTML]{4285f4}{\textbf{**19.95\%}}\\
\addlinespace
\textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{*35.56\%}} & \textcolor[HTML]{4285f4}{\textbf{-5.24\%}} & \textcolor[HTML]{4285f4}{\textbf{-14.05\%}}\\
\textbf{} & \textbf{} & \textbf{backwardation vs. contango} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{**}}\\
\textbf{} & \textbf{volatility} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
\textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{14.39\%}} & \textcolor[HTML]{4285f4}{\textbf{25.92\%}} & \textcolor[HTML]{4285f4}{\textbf{25.94\%}} & \textcolor[HTML]{4285f4}{\textbf{15.13\%}}\\
\textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{16.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.88\%}} & \textcolor[HTML]{4285f4}{\textbf{34.06\%}} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}}\\
\addlinespace
\textbf{} & \textbf{} & \textbf{backwardation vs. contango} & \textcolor[HTML]{4285f4}{\textbf{***}} & \textcolor[HTML]{4285f4}{\textbf{*}} & \textcolor[HTML]{4285f4}{\textbf{***}} & \textcolor[HTML]{4285f4}{\textbf{***}}\\
\bottomrule

@@
